Simple repression draft

### 2020-05-17 doc/paper.tex
Overhaul & split constit inference fig, also hacked p-tile PPC plots

\subsection{Parameter inference for constitutive promoters}
Having established that a one-state bursty model achieves a
Goldilocks level of complexity, we test it more thoroughly on all
the data from constitutive promoters from~\cite{Jones2014}.
\fig{fig:constit_post} shows the results.
\begin{figure}%[h!]
\centering
\includegraphics[width=0.9\textwidth]{../figures/fig2/fig2.pdf}
\caption{\textbf{Constitutive promoter model comparison.}
    (A) ???
    (B) shows the ECDF of the observed population distribution
    of mRNA transcripts under the control of a constitutive lacUV5 promoter.
    Fits of model (1), Poisson, and model (5), negative binomial, are shown.
    \mmnote{Would like to add posterior predictive intervals,
    to give sense of robustness of model.}
    (C) 95\% highest posterior density regions for burst rate $k_i$ and
    mean burst size $b$ for 18 promoters from Brewster 2012. Legend is
    same as (d).
    \mmnote{shared y axis??}
    (D) Burst rate $k_i$ plotted vs.\ binding energy from energy
    matrices from Brewster 2012.
    \mmnote{Need to add fit line still. Also visibility of color palette is very bad, adjust.
    There are 18 data points, maybe 6 colors and 3 glyphs/linestyles
    cycled through? or 9 and 2?}
    }
\label{fig:constit_post}
\end{figure}
\mmnote{Discuss puzzling comparison w/ Chong2014: if supercoiling is the thing, why are my burst sizes all the same but burst rates vary? And why is the duty cycle of my promoter so low, ie., bursts so short? COmpare their fig 7E; their $\beta/\alpha$ is my $k^+/k^-$. They have one or two genes with very small $\beta/\alpha$, does the \textit{galK} locus just happen to be that, or is there a deeper disagreement? Hard to say w/o more data.}

@@

\appendix

@@

model 4 in~\fig{fig:constit_post}

>>>>

\subsection{Parameter inference for constitutive promoters}
Having established that a one-state bursty model achieves a
Goldilocks level of complexity, we test it more thoroughly on all
the data from constitutive promoters from~\cite{Jones2014}.
\fig{fig:constit_post} shows the results.
\begin{figure}%[h!]
\centering
\includegraphics[width=0.9\textwidth]{../figures/fig2/fig2pt1.pdf}
\caption{\textbf{Constitutive promoter posterior
        inference and predictive checks.}
        (A) shows the joint posterior density from MCMC sampling of model 5,
        bursty promoter with negative binomially-distributed steady state.
        (B) shows the ECDF of the observed population distribution
        of mRNA transcripts under the control of a constitutive lacUV5 promoter.
        Posterior predictive percentiles are shown as colored bands for
        model (1), Poisson, and model (5), negative binomial.
        }
\label{fig:uv5_post}
\end{figure}

\begin{figure}%[h!]
\centering
\includegraphics[width=0.9\textwidth]{../figures/fig2/fig2pt2.pdf}
\caption{\textbf{Constitutive promoter model comparison.}
    (A) Joint posterior distributions for burst rate $k_i$ and
    mean burst size $b$ for 18 promoters from Jones 2014.
    Each contour indicates the 95\% highest posterior density
    region for a particular promoter, i.e., on a plot analogous
    to~\fig{fig:uv5_post}, the contour would enclose
    approximately 95\% of the samples, and thus 95\% of the
    probability mass.
    Note that the vertical axis is shared with (B).
    Panel (B) plots the burst rate $k_i$ vs.\ binding energy from energy
    matrices from Brewster 2012.
    The dotted line shows the predicted slope according to
    $\ln k_i/\gamma \sim \text{constant} - \beta\Delta\epsilon_P$,
    described in text.
    }
\label{fig:constit_post}
\end{figure}
\mmnote{Discuss puzzling comparison w/ Chong2014: if supercoiling is the thing, why are my burst sizes all the same but burst rates vary? And why is the duty cycle of my promoter so low, ie., bursts so short? COmpare their fig 7E; their $\beta/\alpha$ is my $k^+/k^-$. They have one or two genes with very small $\beta/\alpha$, does the \textit{galK} locus just happen to be that, or is there a deeper disagreement? Hard to say w/o more data.}

@@

@@

model 5 in~\fig{fig:constit_cartoons}
